---
title: "Report G&#252;i&#241;a"
# date: "6 de junio de 2016"
# output: html_document
output:
  html_document:
    toc: true
    theme: united
date: '`r format(Sys.time(), "%d %B, %Y")`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data
The data set selected is `r DATA_SET$name`.

Original observations `r DATA_SET$original.obs`, and original variables `r DATA_SET$original.var`.

Data set variables:
```{r eval=TRUE, echo=FALSE}
names(DATA_SET$data)
```

Was performed edit data set with 'Delete column':
`r if(DATA$deletevar){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(DATA$deletevar){ print(DATA$vars)}
```

Was performed edit data set with 'Delete nominal values':
`r if(input$dataSetEdit == '2'){"TRUE"} else{"FALSE"}`.


### Preprocessing
Was performed missing values:
`r if(PREPROCESSING$mv){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(PREPROCESSING$mv){ print(paste(PREPROCESSING$missingValues,
                    "missing values were eliminated."))}
```

Was performed LOF:
`r if(PREPROCESSING$out){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(PREPROCESSING$out){ print(PREPROCESSING$outlier) }
```

Was performed Noise Removal:
`r if(PREPROCESSING$noise){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(PREPROCESSING$noise){ print(paste(PREPROCESSING$noiseR,
                      "columns were removed."))}
```

### Transformation
Was performed normalization:
`r if(TRANFORMATION$normalization){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(TRANFORMATION$normalization){ print(paste("Normalization applied:",
                      switch(input$normalizationType,
                        '1' = "Scale Standardization.",
                        '2' = "Normalization 0-1.",
                        '3' = input$type_normalization
                 )))}
```

Was performed PCA:
`r if(TRANFORMATION$pca){ "TRUE"} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(TRANFORMATION$pca){ print(paste("Principal Components:",
                        TRANFORMATION$pcs))}
```

Was performed Attribute Selection:
`r if(TRANFORMATION$sAtributte){ paste("TRUE","Selected attributes:", sep="\n")} else{"FALSE"}`.
```{r eval=TRUE, echo=FALSE}
if(TRANFORMATION$sAtributte){ print(TRANFORMATION$selection.atributte)}
```

### Regression

Was performed Linear Regression:
`r if(is.null(model_lm())){"FALSE"} else{ "TRUE"}`.
```{r model, echo=FALSE}
if(!is.null(model_lm())){ print(paste("Validation:",
                      switch(input$validationType_lm,
                        '1' = "10xCV",
                        '2' = "Test file",
                        '3' = "% test"
                      )))
                      print("Model:")
                      summary(model_lm())
  }
```

```{r plot, fig.height=5, echo=FALSE}
if(!is.null(model_lm())){
  print("Prediction plot:")
  plotValitation_lm1()}
```

Was performed PLS:
`r if(is.null(model_pls())){"FALSE"} else{ "TRUE"}`.
```{r model2, echo=FALSE}
if(!is.null(model_pls())){ print(paste("Validation:",
                      switch(input$validationType_pls,
                        '1' = "10xCV",
                        '2' = "Test file",
                        '3' = "% test"
                      )))
                      print("Model:")
                      summary(model_pls())
  }
```

```{r plot2, fig.height=5, echo=FALSE}
if(!is.null(model_pls())){
  print("Prediction plot:")
  plotPred_pls()}
```

Was performed Ridge:
`r if(is.null(model_ridge())){"FALSE"} else{ "TRUE"}`.
```{r model3, echo=FALSE}
if(!is.null(model_ridge())){ print(paste("Validation:",
                      switch(input$validationType_ridge,
                        '1' = "10xCV",
                        '2' = "Test file",
                        '3' = "% test"
                      )))
                      print("Model:")
                      summary(model_ridge())
  }
```

```{r plot3, fig.height=5, echo=FALSE}
if(!is.null(model_ridge())){
  print("Prediction plot:")
  plotValitation_ridge1()}
```

Was performed RGML:
`r if(is.null(model_rglm())){"FALSE"} else{ "TRUE"}`.
```{r model4, echo=FALSE}
if(!is.null(model_rglm())){ print(paste("Validation:",
                      switch(input$validationType_rglm,
                        '1' = "10xCV",
                        '2' = "Test file",
                        '3' = "% test"
                      )))
                      print("Model:")
                      summary(model_rglm())
  }
```

```{r plot4, fig.height=5, echo=FALSE}
if(!is.null(model_rglm())){
  print("Prediction plot:")
  plotValitation_rglm1()}
```